A Domain Specific Language for SpectreGuard

### 2020-12-09 paper/main.tex
starting related work; 'ghosts of departed proofs

\section{Introduction}
SpectreGuard is provides an abstraction that allows programmers to prevent
speculative access of certain variables.~\cite{SpectreGuard} For
preserving program correctness, static analyses are desirable to prevent
programmers from accidentally successfully compiling code which copies a
``secret'' variable (a variable protected by SpectreGuard) to a ``public''
variable (a variable with no such protection).

To this end, two interrelated static analysis techniques are designed and
implemented. In this paper, we make the following contributions:

\begin{itemize}
\item We describe a small domain specific language embedded in Haskell for representing
  simple C programs (Section~\ref{sec:Syntax}).
\item A code generator which generates C code from this EDSL is outlined
  (Section~\ref{sec:Syntax}).
\item We give a system of types which causes the expression language of this
  EDSL to be statically checked for variable copies that directly leak memory
  from secret variables to public variables (Section~\ref{sec:SensTypes}).
\item Another static analysis procedure is given which can find \textit{indirect}
  leak paths through control structures (Section~\ref{sec:Analysis}). This analysis
  procedure can be applied to EDSL code in the same way as the code generator
  can be applied to EDSL code. The results from this analysis take the form
  of a forest of multiway trees, providing information about these possible
  indirect leaks.
\end{itemize}

@@

\section{Related Work}
...

\section{Future Work}
A further investigation into the tradeoffs and possible additional features of
the information flow analysis is likely to be useful. This could provide a more
accurate and succinct picture to programmers of where leaks are occurring, or
potentially occurring. It is possible that some of these other leak conditions
could be incorporated into the type system, by exploiting the dependent type
features enabled by singletons~\cite{SingletonsPaper} and, in the future, by Dependent Haskell.~\cite{DepHaskSpec}
Dependent types provide a powerful technique for writing programs at a type-level, which
will be executed at compile-time by the type checker.~\cite{CertProg, DepHaskSpec}

@@

\section{Conclusion}
...
%-------------------------------------------------------------------------

>>>>

\section{Introduction}
SpectreGuard is provides an abstraction that allows programmers to prevent
speculative access of certain variables.~\cite{SpectreGuard} For
preserving program correctness, static analyses are desirable to prevent
programmers from accidentally successfully compiling code which copies a
``secret'' variable (a variable protected by SpectreGuard) to a ``public''
variable (a variable with no such protection). To this end, two interrelated static analysis techniques are designed and
implemented.

In this paper, we make the following contributions:

\begin{itemize}
\item We describe a small domain specific language embedded in Haskell for representing
  simple C programs (Section~\ref{sec:Syntax}).
\item A code generator which generates C code from this EDSL is outlined
  (Section~\ref{sec:Syntax}).
\item We give a system of types which causes the expression language of this
  EDSL to be statically checked for variable copies that directly leak memory
  from secret variables to public variables (Section~\ref{sec:SensTypes}).
\item Another static analysis procedure is given which can find \textit{indirect}
  leak paths through control structures (Section~\ref{sec:Analysis}). This analysis
  procedure can be applied to EDSL code in the same way as the code generator
  can be applied to EDSL code. The results from this analysis take the form
  of a forest of multiway trees, providing information about these possible
  indirect leaks.
\item We provide several examples and describe how the system handles them
  (Section~\ref{sec:Examples}).
\end{itemize}

@@

\section{Related Work}
The way that the type-level tagging mechanism works is similar to several other
prior works. One such work is McBride's "Kleisli Arrows of Outrageous Fortune"~\cite{KleisliArrows}. In that paper, an invalid state is unable to be reached as the result of
a similar type-level tag as the \ttt{Sensitivity} tag in the present paper.
However, significantly more machinery is involved in the McBride paper, as
it is necessary to put such a tag on a monadic type. While a monadic type is
used in the present paper (in the form of the \ttt{Cmd} type), this type
does not use a type-level tag. The creation of such machinery is the
main purpose of the McBride paper.

\section{Future Work}
A further investigation into the tradeoffs and possible additional features of
the information flow analysis is likely to be useful. This could provide a more
accurate and succinct picture to programmers of where leaks are occurring, or
potentially occurring. It is possible that some of these other leak conditions
could be incorporated into the type system, by exploiting the dependent type
features enabled by singletons~\cite{SingletonsPaper} and, in the future, by
Dependent Haskell.~\cite{DepHaskSpec} Dependent types provide a powerful
technique for writing programs at a type-level, which will be executed at
compile-time by the type checker.~\cite{CertProg, DepHaskSpec} A more
lightweight technique, which might be able to be applied to allow for more
expressive policies to control of information flow within the type system, would
be the ``ghosts of departed proofs'' design technique.~\cite{DepartedProofs}

@@

\section{Conclusion}

Building upon the SpectreGuard work~\cite{SpectreGuard}, we have constructed
a system which allows the programmer greater assurance that the SpectreGuard
mechanism will not be accidentally circumvented due to certain forms of
leaks from secret variables to public variables. This analysis checks for
both direct copies from a secret variable to a public variable, as well as
a certain class of leaks where control flow depends on a secret variable.

SpectreGuard is a powerful tool for protecting code against Spectre attacks and,
in the present work, we have given tools which provide additional guarantees
that this tool will function as intended.
